An Improvement of Controlling\\Quality of Large Scale Data in Thailand

### 2015-03-30 paper.tex
paper

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}

@@

In order to conduct researches, they have collect precipitation data by installing telemetry systems across Thailand. The telemetry system is a device that is used to collect physical, chemical, and biological data from its various sensors [3]. For instance, river’s water level, rainfall level, humidity, and temperature can be measured. Today, HAII have already installed over 800 telemetry systems. The data collected from the telemetry systems is sent back to HAII’s server by using GPRS cellular network [4].

@@

This paper aim to propose an improvement in outliers and missing pattern algorithms for large-scale water level data. Our main goal is to refine both algorithm to be simple, yet expeditious, while bring out the same results as our previous work. We have reduce running time of outliers algorithm from $O(n^2)$ or $O(n lg n)$, depends on data structures, to $O(n)$. Also, missing pattern is decresed from $O(n^2)$ or $O(n \log{n}^2)$ to $O(n \log{n})$. This can be  done by imitating the clustering result with more simple and fast approach which we will discuss later. The experimental result revealed that our approach significantly cut s down the overall running time in large-scale data.

@@

@@

Currently, Hydro and Agro Informatics Institute (HAII) have already installed over 800 telemetry system across Thailand. Each system send data from its many sensors back to central database every 10 minutes via cellular network. From these figure, we can estimate that there are 3.45 million records of data added to database every month.

\section{Proposed Improved Algorithms}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx, algpseudocode, float}

@@

In order to conduct researches, they have collected precipitation data by installing telemetry systems across Thailand. The telemetry system is a device that is used to collect physical, chemical, and biological data from its various sensors [3]. For instance, river’s water level, rainfall level, humidity, and temperature can be measured. Today, HAII have already installed over 800 telemetry systems. The data collected from the telemetry systems is sent back to HAII’s server by using GPRS cellular network [4].

@@

This paper aim to propose an improvement in outliers and missing pattern algorithms for large-scale water level data. Our main goal is to refine both algorithm to be simple, yet expeditious, while bring out the same results as our previous work. We have reduce running time of outliers algorithm from $O(n^2)$ or $O(n \log{n})$, depends on data structures, to $O(n)$. Also, missing pattern is decresed from $O(n^2)$ or $O(n \log^2{n})$ to $O(n \log{n})$. This can be  done by imitating the clustering result with more simple and fast approach which we will discuss later. The experimental result revealed that our approach significantly cut s down the overall running time in large-scale data.

@@

\section{Large-Scale Water Level Data}

Currently, Hydro and Agro Informatics Institute (HAII) have already installed over 800 telemetry system across Thailand. Figure 4 shows example of location where telemetry systems were installed. Each system send data from its many sensors back to central database every 10 minutes via cellular network. From these numbers, we can estimate that there are 3.45 million records of data added to database every month. Since, HAII have collected precipitation data for over 5 years, we can assume that we are dealing with approximately 207 million records. In previous paper, we use water level data for both outliers and missing pattern algorithms. Moreover, because of the nature of water level in the river, water level's value should be continuous without sudden change.

@@

Our previous work proposed two algorithms to control quality of water-level data, outliers and missing pattern. Both of the algorithms apply clustering technique in order to detect anomaly data and pattern of data. DBSCAN was selected as a clustering algorithms.

\subsection{Outliers Detection Algorithm}
In previous work, we detect outliers by directly applies \textit{DBSCAN} to water-level data. \textit{DBSCAN}'s required parameters, minimum number of points \textit{minpts} and distance epsilon \textit{eps}. Figure \ref{fig:outliers_pseudocode} illustrates pseudocode of outliers detection algorithm.

\begin{figure}[H]
\begin{algorithmic}[1]

\Procedure{Outliers-Detection}{$d$}
\State $minpts\gets1$
\State $eps\gets1.5 $
\State $C\gets\emptyset$\Comment{Set of cluster of data}
\State $N\gets\emptyset$\Comment{Set of noise data}
\State $C, N \gets $\Call{DBSCAN}{$d, minpts, eps$}
\State \Return{$N$}
\EndProcedure
\end{algorithmic}
\caption{Pseudocode of outliers detection algorithm.}
\label{fig:outliers_pseudocode}
\end{figure}

\subsection{Missing Pattern Algorithm}
Lorem Ipsum

\section{Proposed Improved Algorithms}
Lorem Ipsum
